Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reduced references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

We have performed two case studies to evaluate our proposed synthesis approach as described in Table~\ref{tab1}. Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used as our verification engine to compare our approach effectiveness and efficiency. 
The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}. All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
The experiments were performed with a predefined timeout of $240$ minutes.

Only CPAchecker was able to present the optimal sizing of the two case studies: the result came in $50.2$ minutes and $37.2$ minutes, respectively. 
The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 28 from Algorithm~\ref{alg:verification-algorithm}. %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code. 
CBMC and ESBMC produced UNKNOWN result (timeout or out of memory).

%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
 & Case 1 & Case 2\\
\hline
\hline
Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3,900Wh/day \\ Battery autonomy=48h} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4,880Wh/day \\ Battery autonomy=6h}\\
\hline
\makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{UNKNOWN \\(Out of Memory)} & \makecell{UNKNOWN \\(Out of Memory)}\\
\hline
\makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{UNKNOWN \\(Timeout)} & \makecell{UNKNOWN \\(Timeout)} \\
\hline
%UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
%\hline
\makecell{CPAchecker 1.8 \\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\ Property violation line 209: \\NTP=1$\times$330W model (1S)\\NBT=8$\times$105Ah model (2S-4P)\\ Controller 15A/75V\\Inverter 700W, 48V \\ Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\ Property violation line 209:  \\NTP=3$\times$330W model (3S)\\NBT=2$\times$105Ah model (2S)\\ Controller 35A/145V \\ Inverter 1,500VA, 24V \\ Total Cost=US\$ 2,235.57}\\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}

For future work, we will perform additional experiments using other case studies and also compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization. 
Furthermore, we will be provide a larger number of components (panels, batteries, controllers and inverters) to our database to be used by our synthesis engine.
%
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{trindadeThesis_menor}{}

>>>>

We have performed two case studies to evaluate our proposed synthesis approach as described in Table~\ref{tab1}. Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, were used as our verification engine to compare our approach effectiveness and efficiency. 
The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}. All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
The experiments were performed with a predefined timeout of $240$ minutes.
%
Only CPAchecker was able to present the optimal sizing of the two case studies: the result came in $50.2$ minutes and $37.2$ minutes, respectively. 
The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 28 from Algorithm~\ref{alg:verification-algorithm}. %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code. 
CBMC and ESBMC produced UNKNOWN result (timeout or out of memory).
%
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
 & Case 1 & Case 2\\
\hline
\hline
Tool & \makecell{Demand = 501W \\ Peak = 501W \\ Energy=3,900Wh/day \\ Battery autonomy=48h} & \makecell{Demand = 915W \\ Peak = 980W \\ Energy=4,880Wh/day \\ Battery autonomy=6h}\\
\hline
\makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{UNKNOWN \\(Out of Memory)} & \makecell{UNKNOWN \\(Out of Memory)}\\
\hline
\makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{UNKNOWN \\(Timeout)} & \makecell{UNKNOWN \\(Timeout)} \\
\hline
%UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
%\hline
\makecell{CPAchecker 1.8 \\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\ Property violation line 209: \\NTP=1$\times$330W model (1S)\\NBT=8$\times$105Ah model (2S-4P)\\ Controller 15A/75V\\Inverter 700W, 48V \\ Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\ Property violation line 209:  \\NTP=3$\times$330W model (3S)\\NBT=2$\times$105Ah model (2S)\\ Controller 35A/145V \\ Inverter 1,500VA, 24V \\ Total Cost=US\$ 2,235.57}\\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}
%
For future work, we will perform additional experiments using other case studies and also compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization. 
Furthermore, we will be provide a larger number of components (panels, batteries, controllers and inverters) to our database to be used by our synthesis engine.
%
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{trindadeThesis_menor}{}
